---
title: "ryxhw4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ryxhw4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryxhw4)
```


# Introduction

This package contains useful functions to calculate the correlation between two or more variables. It was created as part of a homework assignment for QAC356.

# Functions

The package has 4 functions. One core function ryx() and 3 generic S3 functions (print.ryx(), summary.ryx(), and plot.ryx()) to display the output of the core function.

## ryx()

The ryx function is the core of this package. It takes a dataframe and specified variables and calculates the correlations between the variables. The function returns a list of 3 containing the variables used and a dataframe of the correlation results.

```{r}
data(mtcars)
x <- ryx(mtcars, y = "mpg", x = c("wt", "disp"))
x
```

## print.ryx()

The print.ryx function displays the output of the core ryx function in a simple table.

```{r}
print(x)
```

## summary.ryx()

The summary.ryx function displays the output of the core ryx function in words

```{r}
summary(x)
```

## plot.ryx()

The plot.ryx function displays the output of the core ryx function in a dotchart graph

```{r}
plot(x)
```

